Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-01-24 manuscripts/paper-1/main.tex
work on paper structure; comment out some parts

\documentclass[9pt,conference]{IEEEtran}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\graphicspath{{./images/}}

@@

@@

@@

@@

    \subsection{Possibility of States}
    \subsection{Context of Digital Twin}
    \subsection{Quality of Digital Twin}

    \subsection{Research objectives}
    Find an approach to assess the quality of Digital twins

    \subsection{Research questions}
    \label{section: Research Questions}
    What is a digital twin?
    What is the quality of digital twins? 
    What is good quality?
    What is bad quality? 
    What is the impact of good quality? 
    What is the impact of bad quality? W
    What are typical quality issues? 
    How to assess quality?

    \subsection{Scientific contributions}
    Literature review (see Section~\ref{section: literature}), case study (see Section~\ref{section: Research Questions})...

    \section{Literature review}
    \label{section: literature}
    Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
    how the digital twin quality is mentioned and assessed within the academic dissertations.

@@

    He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin ~\cite{Jones2020}.
    (Existing literature does at most partially solve our problem!)

    \section{Our framework}
    \label{section:framework_1}
    TODO

@@

    \section{Case study (FELICE)}
    \label{section:case}
    TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)

@@

    \subsection{Summary}~\label{section:case_summary}
    TODO

>>>>

\documentclass[9pt,conference]{IEEEtran}

\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\graphicspath{{./images/}}

@@

    \subsection{Research objective}
    Find an approach to assess the quality of Digital twins~\cite{Jones2020}

    \subsection{Research question}\label{section: Research Questions}
    What is quality of digital twins?

    \subsection{Research methodology}
    TODO

    \section{State of the art on quality}
    TODO

    \subsection{Product quality}
    Most generic (e.g.~House of quality, ...)

    \subsection{Software quality}
    Medium (e.g.~ISO/IEC 9126 and ISO 25010, ...)

    \subsection{Digital twin quality}
    Most specific (a bit more research here!)

    \section{Initial approach in the FELICE project}
    Inspired by ISO 25010...

    \subsection{First criterion: Correctness}

    \subsubsection{Definition}
    Car vs airplane (with nice pictures!)

    \subsubsection{Motivation}
    TODO

    \subsubsection{Findings from FELICE}
    TODO

    \subsection{Second criterion: Completeness}

    \subsubsection{Definition}
    Car vs engine (with nice pictures!)

    \subsubsection{Motivation}
    TODO

    \subsubsection{Findings from FELICE}
    TODO

    \subsection{Third criterion: Fidelity}

    \subsubsection{Definition}
    Linear vs differential (with nice pictures!)

    \subsubsection{Motivation}
    TODO

    \subsubsection{Findings from FELICE}
    TODO

    \subsection{Fourth criterion: Efficiency}

    \subsubsection{Definition}
    1ms vs 1min (with nice pictures!)

    \subsubsection{Motivation}
    TODO

    \subsubsection{Findings from FELICE}
    TODO

    \subsection{Fifth criterion: Evolvability}

    \subsubsection{Definition}
    Effort to adapt the digital twin to new circumstances (e.g.\ add new machine, replace machine, etc.)

    \subsubsection{Motivation}
    TODO

    \subsubsection{Findings from FELICE}
    TODO

    \begin{comment}
        \section{Whatever}

@@

        \subsubsection{How it is defined?}

@@

        \subsubsection{Why it is problematic?}

        TODO

@@

        \subsection{Possibility of States}
        \subsection{Context of Digital Twin}
        \subsection{Quality of Digital Twin}
    \end{comment}

    \begin{comment}
        \section{Literature review}
        \label{section: literature}
        Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
        how the digital twin quality is mentioned and assessed within the academic dissertations.

@@

        He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin ~\cite{Jones2020}.
        (Existing literature does at most partially solve our problem!)
    \end{comment}

    \section{Future approach in the FELICE project}
    \label{section:framework_1}
    TODO

@@

    \begin{comment}
        \section{Case study (FELICE)}\label{section:case}
        TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)

@@

        \subsection{Summary}~\label{section:case_summary}
        TODO
    \end{comment}
